A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2020-09-04 Analysis/nat_stories_spr.Rmd
talk edits

```{r}
#mean by subject for each word
d_lm <- spr_data %>% group_by(word, txl_center, ngram_center, grnn_center, freq_center, length_center,
                                        past_c_txl, past_c_ngram, past_c_grnn, past_c_freq, past_c_length, Word_ID) %>% 
  summarize(mean_rt=mean(rt))
```

@@

ngram_data <- spr_data %>% select(rt, surprisal=ngram_surp, prev_surp=past_ngram, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            ) %>% mutate(model="5-gram")

grnn_data <- spr_data %>% select(rt, surprisal=grnn_surp, prev_surp=past_grnn, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            )%>% mutate(model="GRNN")

txl_data <- spr_data %>% select(rt, surprisal=txl_surp, prev_surp=past_txl, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            ) %>% mutate(model="TXL")

@@

```{r gams}
gam_ngram_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=ngram_data, method="REML")

gam_grnn_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=grnn_data, method="REML")

gam_txl_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=txl_data, method="REML")

@@

ggsave("../Papers/gam.pdf", width=4, height=2.3, unit="in")

>>>>

```{r}
spr_data <- read_rds("spr.rds")
#mean by subject for each word
d_lm <- spr_data %>% group_by(word, txl_center, ngram_center, grnn_center, freq_center, length_center,
                                        past_c_txl, past_c_ngram, past_c_grnn, past_c_freq, past_c_length, Word_ID) %>% 
  summarize(mean_rt=mean(rt))
```

@@

# trying with semi-summarized data, b/c otherwise it takes forever

# ngram_data <- spr_data%>% select(rt, surprisal=ngram_surp, prev_surp=past_ngram, 
#                                             freq=freq_center, len=length_center,
#                                             prev_freq=past_c_freq, prev_len=past_c_length
#                                             ) %>% mutate(model="5-gram")
# 
# grnn_data <- spr_data %>% select(rt, surprisal=grnn_surp, prev_surp=past_grnn, 
#                                             freq=freq_center, len=length_center,
#                                             prev_freq=past_c_freq, prev_len=past_c_length
#                                             )%>% mutate(model="GRNN")
# 
# txl_data <- spr_data %>% select(rt, surprisal=txl_surp, prev_surp=past_txl, 
#                                             freq=freq_center, len=length_center,
#                                             prev_freq=past_c_freq, prev_len=past_c_length
#                                             ) %>% mutate(model="TXL")

@@

```{r gams}
# gam_ngram_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=ngram_data, method="REML")
# 
# gam_grnn_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=grnn_data, method="REML")
# 
# gam_txl_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=txl_data, method="REML")

@@

ggsave("../Papers/gam-spr.pdf", width=4, height=2.3, unit="in")

### 2020-09-04 Papers/Amlap_2020_talk/amlap_2020_talk.tex
modify graph
talk edits

%Add some restrictions:
%\begin{itemize}
%\item Restrict to a list of possible distractors
%\item Only consider length, frequency matches
%\end{itemize}
%	
\end{frame}
%
\begin{frame}{Does it work?} 
\pause
\vskip -2em
{\large Yes, at least well enough.} \pause
\begin{itemize}
	\item Sometimes generates plausible distractors. \pause
	\item A-maze results comparable with G-maze {\small(Boyce et al 2020, Sloggett et al 2020)} \pause 
\end{itemize} 
\medskip
\centering

\includegraphics[width=.7\textwidth]{../a_all.pdf}
\end{frame}
%
\begin{frame}{Maze Made Easy}

@@

\end{frame}
%\begin{frame}{Surprisal Effects}
%	Takeaways: \pause
%	\begin{itemize}
%		\item Minimal frequency effects (consistent with Shain 2019) \pause
%		\item Long RTs \pause
%		\item Large effects of Length, Surprisal \pause
%		\item Very little spillover \pause
%	\end{itemize}
%	
%	Model comparison: GRNN is best, but TXL complementary
%\end{frame}

\begin{frame}{Why such large effects?}
	\pause
	Bayesian reader framework: Look at words long enough to ID with some threshold of certainty \pause

>>>>

%Add some restrictions:
%\begin{itemize}
%\item Restrict to a list of possible distractors
%\item Only consider length, frequency matches
%\end{itemize}
%	
\end{frame}
%
\begin{frame}{Does it work?} 
\pause
%\vskip -2em
{\large Yes, at least well enough.} \pause
\begin{itemize}
	\item Sometimes generates plausible distractors. \pause
	\item A-maze results comparable with G-maze {\small(Boyce et al 2020, Sloggett et al 2020)}
\end{itemize} 
\end{frame}

\begin{frame}{Does it work?} 
	%\vskip -2em
		\small
	From ``Maze Made Easy'' (Boyce et al 2020)
	\medskip

	\includegraphics[width=\textwidth]{../spr_g_amaze.pdf}

		{\footnotesize Error bars: 95\% CI}

\end{frame}
%
\begin{frame}{Maze Made Easy}

@@

\end{frame}
\begin{frame}{Surprisal Effects}
	Takeaways: \pause
	\begin{itemize}
		\item Minimal frequency effects (consistent with Shain 2019) \pause
		\item Large effects of Length, Surprisal \pause
		\item Very little spillover \pause
	\end{itemize}
%	
	Model comparison: GRNN is best, but TXL complementary
\end{frame}

\begin{frame}{Why such large effects?}
	\pause
	Bayesian Reader (Norris 2006): Look at words long enough to ID with some threshold of certainty \pause
